\begin{frame}{Macros}
\begin{itemize}
\item Writing programs that generate or manipulate programs as their data.
\item A program that manipulates code.
\item Code-generating programs are sometimes called meta-programs; writing such programs
    is called meta-programming.
\end{itemize}
\end{frame}

\begin{frame}{Textual macro languages}
\begin{itemize}
\item Textual Macros are macros that directly affect the text of the programming 
    language without knowing about or dealing with the meaning of the language \emph{e.g.} C 
    preprocessor and the M4 macro processor \cite{macrosibm}. 
\end{itemize}
\end{frame}

\begin{frame}[fragile]{C preprocessor SWAP}
\inputminted[mathescape,
           linenos,
           numbersep=5pt,
           frame=lines,
           bgcolor=White,
           fontsize=\scriptsize,
           linenos,
           framesep=2mm]{c++}
           {/Users/lalanne/MyCode/GitHubProjects/MP_Talk/macro_swap.cpp} 
\end{frame}

\begin{frame}{Advantages}
\begin{itemize}
\item function call too much overhead for this simple operation (myth).
\item you would have to code different functions for different types.
\end{itemize}
\end{frame}

\begin{frame}{Disadvantages}
\begin{itemize}
\item you do not get any type of type safety.
\item if you pass tmp\_c as an argument the macro will fail.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{C preprocessor MIN}
\inputminted[mathescape,
           linenos,
           numbersep=5pt,
           frame=lines,
           bgcolor=White,
           fontsize=\scriptsize,
           linenos,
           framesep=2mm]{c++}
           {/Users/lalanne/MyCode/GitHubProjects/MP_Talk/macro_min.cpp} 
\end{frame}

\begin{frame}{The MIN case}
\begin{itemize}
\item necessary parenthesis (operator precedence).
\item When one of the arguments is a function is going to be call twice. (performance, duplicated calculation).
\end{itemize}
\end{frame}





